PWNCAT2

### 2012-02-07 pwncatalog/PWNCAT2/paper/sections/results.tex
update

Results goes here\ldots

\tabref{all_energy} shows the results of the all energy analysis of the off-peak emission for each pulsar.

\tabref{each_energy} shows the results of the analysis in separate energy bins of each pulsar.

\tabref{cutoff_test} shows the results of the cutoff test for pulsars with significant low-energy emission.

@@

The localization results are in \tabref{localization}

>>>>

First, we tested the sources to see if they
were spatially extended. The localization results are in \tabref{localization}.

Next, we performed a spectral analysis over all energy using the best
fit morphology. \tabref{all_energy} shows the results of the all energy
analysis of the off-peak emission for each pulsar.

Next, we fit a powerlaw independently in each energy
bin. \tabref{each_energy} shows the results of the analysis in separate
energy bins of each pulsar.

Finally, we tested sources to see which were
variable. \tabref{cutoff_test} shows the results of the cutoff test for
pulsars with significant low-energy emission.

@@
